---
title: "The goal of ggols is to ..."
subtitle: ""
author: "Gina Reynolds"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r, include = F}
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
knitr::opts_chunk$set(fig.width = 6, fig.height = 4, message = F, warning = FALSE, comment = "", cache = F)

options(tibble.print_min = 55)
options(knitr.duplicate.label = "allow")
options(width=300) # prevents data wrapping
```


```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 70%}

@media print {
  .has-continuation {
    display: block;
  }
}

code.r.hljs.remark-code{
  position: relative;
  overflow-x: hidden;
}


code.r.hljs.remark-code:hover{
  overflow-x:visible;
  width: 500px;
  border-style: solid;
}
```


<!-- README.md is generated from README.Rmd. Please edit that file -->

---




```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = F
)
```

# ggols

<!-- badges: start -->
<!-- badges: end -->

The goal of ggols is to ...

## Installation

You can install the released version of ggols from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("ggols")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("EvaMaeRey/ggols")
```

---

## ggxmean gives us all the geom_lm_* functions

---


`r flipbookr::chunk_reveal("example", left_assign = "detect")`


```{r example, include = FALSE}
library(tidyverse)
library(ggxmean)

ggplot(palmerpenguins::penguins) +
  aes(x = bill_depth_mm, y = bill_length_mm) +
  geom_point() +
  geom_lm() +
  geom_lm_intercept(color = "blue") +
  geom_lm_intercept_label(hjust = -.2) +
  geom_lm_conf_int() +
  geom_lm_residuals() +
  geom_lm_fitted() +
  geom_lm_formula() + 
  ggols:::geom_lm_rsquared() #should be moved to ggxmean
```

---

# Visualization, adding indicator var

---


`r flipbookr::chunk_reveal("indicator", left_assign = "detect")`


```{r indicator, include = FALSE}
library(ggols)

ggplot(cars) +
  aes(x = speed, y = dist, indicator = dist > 30,
  color = dist > 30) +
  geom_point() +
  geom_lm_indicator() +
  geom_lm_indicator_intercept(color = "blue") +
  geom_lm_indicator_intercept_label(hjust = -.2) +
  geom_lm_indicator_conf_int() +
  geom_lm_indicator_residuals() +
  geom_lm_indicator_fitted() +
  geom_lm_indicator_formula() +
  geom_lm_indicator_rsquared()
```


---

# Visualization, adding x*indicator interaction


---


`r flipbookr::chunk_reveal("interaction", left_assign = "detect")`


```{r interaction, include = FALSE}
ggplot(cars) +
  aes(x = speed, y = dist, indicator = dist > 30,
  color = dist > 30) +
  geom_point() +
  geom_lm_interaction() +
  geom_lm_interaction_intercept(color = "blue") +
  geom_lm_interaction_intercept_label(hjust = -.2) +
  geom_lm_interaction_conf_int() +
  geom_lm_interaction_residuals() +
  geom_lm_interaction_fitted() +
  geom_lm_interaction_formula() +
  geom_lm_interaction_rsquared()
```

---

# Visualization, and two indicator variables (parallel slopes)


---


`r flipbookr::chunk_reveal("int2", left_assign = "detect")`


```{r int2, include = FALSE}
ggplot(palmerpenguins::penguins) +
  aes(x = bill_length_mm, y = bill_depth_mm, 
      indicator = species, indicator2 = sex,
      color = species, shape = sex) +
  geom_point() +
  geom_lm_indicator2() +
  geom_lm_indicator2_conf_int() + 
  geom_lm_indicator2_residuals() +
  geom_lm_indicator2_fitted() +
  geom_lm_indicator2_formula() +
  geom_lm_indicator2_rsquared() +
  NULL
```

---

`r flipbookr::chunk_reveal("int3", left_assign = "detect")`


```{r int3, include = F}
last_plot() + 
  geom_lm_indicator2_intercept(color = "blue") +
  geom_lm_indicator2_intercept_label(hjust = -.2)
```
